Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-06 ms.tex
Added some text to conclusions

\newcommand{\wprp}{w_{\mathrm{p}}}
\newcommand{\rp}{r_{\mathrm{p}}}
\newcommand{\magr}{M_r}
\bibliographystyle{mn2e}

@@

>>>>

\newcommand{\wprp}{w_{\mathrm{p}}}
\newcommand{\rp}{r_{\mathrm{p}}}
\newcommand{\magr}{M_r}

\newcommand{\bit}{\begin{itemize}}
\newcommand{\eit}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}

\bibliographystyle{mn2e}

@@

We have re-analyzed the SDSS DR7 measurements of projected galaxy clustering,  $\wprp,$ and number density, $n_{\rm g},$ originally published in \citet{zehavi_etal11}. Our work is especially novel in that we provide the first quantitative constraints on assembly bias derived from the Decorated HOD, an extension to the traditional HOD introduced in \citet{hearin_etal16} developed for exactly this purpose. 
We enumerate our most important conclusions below. 
\ben
\item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$
\item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we sample. 
\een
As $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7, it is likely that further improvements on assembly bias constraints at low-redshift will require additional observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc.
